---
title: "Attention and prediction on V1/C1"
author: "Max Van Migem"
date: "2024-07-03"
---

```{r packages}
library(car)
library(tidyr)
library(lme4)
library(rstan)
library(brms)
library(lmerTest)
library(optimx)

```

## load data

```{r data}
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p3_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/c1_long_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/c1_long_nosubset_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/c1_galat_long_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/c1_oc_fix_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/c1_oc_var_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p3a_oc_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p3b_oc_df.csv')
df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p1_oc_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p2_oc_df.csv')

```
```{r data}
df$subject <- as.factor(df$subject)
df$attention <- as.factor(df$attention)
df$expectation <- as.factor(df$expectation)
df$visual_field <- as.factor(df$visual_field)
df$rescaled_genamp = scale(df$general_amp)
df$rescaled_tailamp = scale(df$tailored_amp)

options(contrasts = c("contr.sum", "contr.poly"))

df_regular <- subset(df, expectation == 'regular')
df_odd <- subset(df, expectation == 'odd')
df_attended <- subset(df, attention == 'attended')
df_unattended <- subset(df, attention == 'unattended')
df_up <- subset(df, visual_field == 'up')
df_down <- subset(df, visual_field == 'down')
```

## the full model
```{r}
# tailored_amp ultra_amp general_amp


f1 <- tailored_amp ~ 1 + expectation + attention + visual_field + 
                       attention*expectation + attention*visual_field + expectation*visual_field +
                  (1 + attention + expectation + visual_field | subject)

f2 <- tailored_amp ~ 1 + expectation + attention + visual_field + 
                       attention*expectation + attention*visual_field + expectation*visual_field +
                  (1 | subject)

fit.c1_1 <- lmer(f1,data = df, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
fit.c1_2 <- lmer(f2,data = df, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
# fit.c1_gen <- brm(f,data = df, family = gaussian())
anova(fit.c1_1,fit.c1_2)
summary(fit.c1_1)
contrasts(df$attention)
contrasts(df$expectation)
contrasts(df$visual_field)
```
```{r}
f <- tailored_amp ~ 1 + expectation + attention  + attention*expectation +
                  (1 + attention + expectation | subject)

# fit.c1_up <- lmer(f,data = df_up, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
fit.c1_up <- brm(f,data = df_up, family = gaussian())
summary(fit.c1_up)
contrasts(df$attention)
contrasts(df$expectation)
```
```
```{r}
f <- tailored_amp ~ 1 + expectation + attention  + attention*expectation +
                  (1 + attention + expectation | subject)

# fit.c1_up <- lmer(f,data = df_down, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
fit.c1_up <- brm(f,data = df_down, family = gaussian())
summary(fit.c1_down)
contrasts(df$attention)
contrasts(df$expectation)
```
```

# P3 analysis

## full model
```{r}
fit.p3.full <-  lmer(contra_p1 ~ 1 + attention + expectation + attention*expectation +
                           (1 +attention | subject),
  data = df, 
  control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))

summary(fit.p3.full)
contrasts(df$attention)
contrasts(df$expectation)
```

## the attended model
```{r}
fit.p3.attended <-  lmer(mean_amp ~ 1 + expectation +
                           (1 | subject),
  data = df_attended, 
  control = lmerControl(optimizer = c("Nelder_Mead"), optCtrl=list(maxfun=2e6)))

summary(fit.p3.attended)
contrasts(df_attended$attention)
contrasts(df_attended$expectation)
```

## the unattended model
```{r}
fit.p3.unattended <-  lmer(mean_amp ~ 1 + expectation +
                           (1 | subject),
  data = df_unattended, 
  control = lmerControl(optimizer = c("Nelder_Mead"), optCtrl=list(maxfun=2e6)))

summary(fit.p3.unattended)
contrasts(df$attention)
contrasts(df$expectation)z

```

## the unattended model
```{r}
fit.p3.regular <-  lmer(mean_amp ~ 1 + attention +
                           (1 | subject),
  data = df_odd, 
  control = lmerControl(optimizer = c("Nelder_Mead"), optCtrl=list(maxfun=2e6)))

summary(fit.p3.regular)
contrasts(df$attention)
contrasts(df$expectation)

```