---
title: "Attention and prediction on V1/C1"
author: "Max Van Migem"
date: "2024-07-03"
---

```{r packages}
library(car)
library(tidyr)
library(lme4)
library(lmerTest)
library(optimx)
```

## load data

```{r data}
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p3_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/c1_long_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/c1_galat_long_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/c1_oc_fix_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/c1_oc_var_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p3a_oc_df.csv')
df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p3b_oc_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p1_oc_df.csv')

```
```{r data}
df$subject <- as.factor(df$subject)
df$attention <- as.factor(df$attention)
df$expectation <- as.factor(df$expectation)
# df$visual_field <- as.factor(df$visual_field)

options(contrasts = c("contr.sum", "contr.poly"))

df_regular <- subset(df, expectation == 'regular')
df_odd <- subset(df, expectation == 'odd')
df_attended <- subset(df, attention == 'attended')
df_unattended <- subset(df, attention == 'unattended')
# df_up <- subset(df, visual_field == 'up')
# df_down <- subset(df, visual_field == 'down')
```

## the full model
```{r}
# tailored_amp ultra_amp general_amp
fit.c1_gen <- lmer(P3a ~ 1 + expectation + attention + visual_field + 
                            attention*expectation + attention*visual_field + expectation*visual_field +
                           (1 | subject) +(expectation | subject) + (attention | subject) + (visual_field | subject),
  data = df, 
  control = lmerControl(
  optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
summary(fit.c1_gen)
contrasts(df$attention)
contrasts(df$expectation)
contrasts(df$visual_field)
```
```{r}
fit.c1_up <- lmer(baseline_corrected ~ 1 + expectation + attention + attention*expectation +
                           (1| subject) + (attention | subject) + (expectation| subject),
  data = df_up, 
  control = lmerControl(
  optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))

summary(fit.c1_up)
contrasts(df$attention)
contrasts(df$expectation)
```
```
```{r}
fit.c1_down <- lmer(baseline_corrected ~ 1 + expectation + attention + attention*expectation +
                           (1| subject) + (attention | subject)+ (expectation| subject) ,
  data = df_down, 
  control = lmerControl(
  optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
summary(fit.c1_down)
contrasts(df$attention)
contrasts(df$expectation)
```

# P3 analysis

## full model
```{r}
fit.p3.full <-  lmer(P3b ~ 1 + attention + expectation + attention*expectation +
                           (1 | subject)+ (attention | subject)+ (expectation| subject),
  data = df, 
  control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))

summary(fit.p3.full)
contrasts(df$attention)
contrasts(df$expectation)
```

## the attended model
```{r}
fit.p3.attended <-  lmer(contra_p1 ~ 1 + expectation +
                           (1 | subject),
  data = df_attended, 
  control = lmerControl(optimizer = c("Nelder_Mead"), optCtrl=list(maxfun=2e6)))

summary(fit.p3.attended)
contrasts(df_attended$attention)
contrasts(df_attended$expectation)
```

## the unattended model
```{r}
fit.p3.unattended <-  lmer(contra_p1 ~ 1 + expectation +
                           (1 | subject),
  data = df_unattended, 
  control = lmerControl(optimizer = c("Nelder_Mead"), optCtrl=list(maxfun=2e6)))

summary(fit.p3.unattended)
contrasts(df$attention)
contrasts(df$expectation)z

```

## the unattended model
```{r}
fit.p3.regular <-  lmer(contra_p1 ~ 1 + attention +
                           (1 | subject),
  data = df_odd, 
  control = lmerControl(optimizer = c("Nelder_Mead"), optCtrl=list(maxfun=2e6)))

summary(fit.p3.regular)
contrasts(df$attention)
contrasts(df$expectation)

```