---
title: "Attention and prediction on V1/C1"
author: "Max Van Migem"
date: "2024-07-03"
---

```{r packages}
library(car)
library(pbkrtest)
library(lmerTest)
library(lme4)
library(optimx)
library(performance)
library(emmeans)
# library(brms)
# library(rstan)

```

## load data

```{r data}
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p3_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/c1_long_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/c1_oc_fix_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/c1_oc_var_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p3a_oc_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p3b_oc_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p1_oc_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p1_oc_nc_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/n1_oc_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/nc_n1_oc_df.csv')
# df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/p2_oc_df.csv')
df <- read.csv('C:/Users/mvmigem/Documents/data/project_1/compiled_dataframes/behaviour.csv')

df <- subset(df, !subject %in% c(3, 14, 20))

```
```{r data}
df$subject <- as.factor(df$subject)
df$participant <- as.factor(df$participant)
df$attention <- as.factor(df$attention)
df$expectation <- as.factor(df$expectation)
df$visual_field <- as.factor(df$visual_field)
df$hemisphere <- as.factor(df$hemisphere)
# df$rescaled_genamp = scale(df$general_amp)
# df$rescaled_tailamp = scale(df$tailored_amp)
# df$baseline_corrected = scale(df$baseline_corrected)

options(contrasts = c("contr.sum", "contr.poly"))

df_regular <- subset(df, expectation == 'regular')
df_odd <- subset(df, expectation == 'odd')
df_attended <- subset(df, attention == 'attended')
df_unattended <- subset(df, attention == 'unattended')
df_att_odd <- subset(df_odd, attention == 'attended')
df_att_reg <- subset(df_regular, attention == 'attended')
df_ipsi <- subset(df, hemisphere == 'ipsi')
df_contra <- subset(df, hemisphere == 'contra')
# df_up <- subset(df, visual_field == 'up')
# df_down <- subset(df, visual_field == 'down')
```

## the full model
```{r}
# tailored_amp ultra_amp general_amp, baseline_corrected

f1 <- tailored_amp ~ 1 + expectation + attention + visual_field + 
                       attention*expectation + attention*visual_field + expectation*visual_field + attention*expectation*visual_field +
                  (1 + attention + expectation + visual_field | subject)

f2 <- baseline_corrected ~ 1 + expectation + attention + visual_field + 
                       attention*expectation + attention*visual_field + expectation*visual_field +
                  (1 | subject)

fit.c1_1 <- lmer(f1,data = df, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
fit.c1_2 <- lmer(f2,data = df, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
fit.c1_gen <- brm(f1,data = df)
anova(fit.c1_1,fit.c1_2)
summary(fit.c1_1)
summary(fit.c1_2)
summary(fit.c1_gen)
contrasts(df$attention)
contrasts(df$expectation)
contrasts(df$visual_field)
confint()
```

```{r}
# tailored_amp ultra_amp general_amp

anova(fit.c1_1,fit.c1_2)
summary(fit.c1_1)
summary(fit.c1_2)
plot(fit.c1_1)
qqnorm(residuals(fit.c1_1))
bootstrap|> tidy()
bootstrap <- PBmodcomp(fit.c1_1,fit.c1_2,nsim=1000)
check_model(fit.c1_1)
check_model(fit.c1_2)
ysummary(bootstrap)

```

```{r}
f1 <- tailored_amp ~ 1 + expectation + attention  + attention*expectation +
                  (1 + attention + expectation | subject)

f2 <- tailored_amp ~ 1 + expectation + attention +  attention*expectation + 
                  (1 |subject)

fit.c1_up1 <- lmer(f1,data = df_up, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))

fit.c1_up2 <- lmer(f2,data = df_up, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
# fit.c1_up <- brm(f,data = df_up, family = gaussian())
summary(fit.c1_up1)
summary(fit.c1_up2)
anova(fit.c1_up1,fit.c1_up2)
contrasts(df$attention)
contrasts(df$expectation)
```
```
```{r}
f1 <- tailored_amp ~ 1 + expectation + attention  + attention*expectation +
                  (1 + attention + expectation | subject)

f2 <- tailored_amp ~ 1 + expectation + attention +  attention*expectation + 
                  (1 |subject)

fit.c1_down1 <- lmer(f1,data = df_down, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))


# fit.c1_up <- brm(f,data = df_up, family = gaussian())
summary(fit.c1_down1)


summary(fit.c1_down2)
anova(fit.c1_down1,fit.c1_down2)
contrasts(df$attention)
contrasts(df$expectation)
```
```


## the P1 model also N1 and P2 if you load other df
```{r}
# tailored_amp ultra_amp general_amp


f1 <- yhat ~ 1 + expectation + attention + hemisphere +
                       attention*expectation + attention*hemisphere + expectation*hemisphere + attention*expectation*hemisphere +
                  (1 + attention + expectation + hemisphere | subject)

f2 <- yhat ~ 1 + expectation + attention +
                       attention*expectation+
                  (1 + attention + expectation | subject)

fit.c1_1 <- lmer(f1,data = df, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
fit.c1_2 <- lmer(f2,data = df_contra, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
# fit.c1_gen <- brm(f,data = df, family = gaussian())
check_model(fit.c1_1)
check_model(fit.c1_2)
anova(fit.c1_1,fit.c1_2)
summary(fit.c1_1)
summary(fit.c1_2)
contrasts(df$attention)
contrasts(df$expectation)
contrasts(df$visual_field)
confint(fit.c1_1,method = "Wald")

```
```{r}

mean(df_attended$yhat, na.rm = TRUE)
sd(df_attended$yhat, na.rm = TRUE)
mean(df_unattended$yhat, na.rm = TRUE)
sd(df_unattended$yhat, na.rm = TRUE)

mean(df_odd$P3b, na.rm = TRUE)
sd(df_odd$P3b, na.rm = TRUE)
mean(df_regular$P3b, na.rm = TRUE)
sd(df_regular$P3b, na.rm = TRUE)

mean(df_att_odd$P3b, na.rm = TRUE)
sd(df_att_odd$P3b, na.rm = TRUE)
mean(df_att_reg$P3b, na.rm = TRUE)
sd(df_att_reg$P3b, na.rm = TRUE)

```


```{r}
f1 <- yhat ~ 1 + expectation  + hemisphere + expectation*hemisphere +
                  (1 + expectation | subject)

fit.p2_1 <- lmer(f1,data = df_unattended, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
# fit.c1_gen <- brm(f,data = df, family = gaussian())
summary(fit.p2_1)

confint(fit.p3_2, method ="Wald")
contrasts(df$attention)
contrasts(df$expectation)

```

```{r}
f1 <- yhat ~ 1 + attention  + hemisphere + attention*hemisphere +
                  (1 + attention  | subject)

fit.p2_1 <- lmer(f1, data = df_regular, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
# fit.c1_gen <- brm(f,data = df, family = gaussian())
summary(fit.p2_1)

confint(fit.p3_2, method ="Wald")
contrasts(df$attention)
contrasts(df$expectation)

```
# P3 analysis

## full model
```{r}
df <- na.omit(df)
f1 <- P3b ~ 1 + expectation + attention +
                       attention*expectation +
                  (1 + attention + expectation | subject)

f2 <- P3b ~ 1 + expectation + attention +
                       attention*expectation+
                  (1 | subject)

fit.p3_1 <- lmer(f1,data = df, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
fit.p3_2 <- lmer(f2,data = df, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
# fit.c1_gen <- brm(f,data = df, family = gaussian())
anova(fit.p3_1,fit.p3_2)
summary(fit.p3_1)
summary(fit.p3_2)
confint(fit.p3_2, method ="Wald")
contrasts(df$attention)
contrasts(df$expectation)
emmeans_f1 <- emmeans(fit.p3_2, ~ expectation * attention)
pairs(emmeans_f1, adjust = "tukey")
```
```{r}
# tailored_amp ultra_amp general_amp

anova(fit.p3_1,fit.p3_2)
summary(fit.p3_1)
summary(fit.p3_2)

bootstrap|> tidy()
bootstrap <- PBmodcomp(fit.p3_1,fit.p3_2,nsim=1000)
check_model(fit.p3_1)
check_model(fit.p3_2)
summary(bootstrap)

```

## the attended model
```{r}
f1 <- P3b ~ 1 + expectation  +
                  (1 + expectation | subject)

f2 <- P3b ~ 1 + expectation +
                  (1 | subject)

fit.p3_1 <- lmer(f1,data = df_attended, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
fit.p3_2 <- lmer(f2,data = df_attended, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
# fit.c1_gen <- brm(f,data = df, family = gaussian())
anova(fit.p3_1,fit.p3_2)
summary(fit.p3_1)
summary(fit.p3_2)
confint(fit.p3_2, method ="Wald")
contrasts(df$attention)
contrasts(df$expectation)

```

## the unattended model
```{r}
f1 <- P3b ~ 1 + expectation  +
                  (1 + expectation | subject)

f2 <- P3b ~ 1 + expectation +
                  (1 | subject)

fit.p3_1 <- lmer(f1,data = df_unattended, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
fit.p3_2 <- lmer(f2,data = df_unattended, control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
# fit.c1_gen <- brm(f,data = df, family = gaussian())
anova(fit.p3_1,fit.p3_2)
summary(fit.p3_1)
summary(fit.p3_2)
confint(fit.p3_2, method ="Wald")
contrasts(df$attention)
contrasts(df$expectation)

```

## the regular model
```{r}
fit.p3.regular <-  lmer(P3b ~ 1 + attention +
                           (1 | subject),
  data = df_regular, 
  control = lmerControl(optimizer = c("Nelder_Mead"), optCtrl=list(maxfun=2e6)))

summary(fit.p3.regular)
contrasts(df$attention)
contrasts(df$expectation)

```
## the odd model
```{r}
fit.p3.regular <-  lmer(P3b ~ 1 + attention +
                           (1 attention| subject),
  data = df_odd, 
  control = lmerControl(optimizer = c("Nelder_Mead"), optCtrl=list(maxfun=2e6)))

summary(fit.p3.regular)
contrasts(df$attention)
contrasts(df$expectation)

```
## the behaviour model
```{r}
fit.behaviour <-  lmer(rt ~ 1 + attention +
                           (1 | participant),
  data = df, 
  control = lmerControl(optimizer = c("Nelder_Mead"), optCtrl=list(maxfun=2e6)))
confint(fit.behaviour, method ="Wald")
summary(fit.behaviour)
contrasts(df$attention)

```